\documentclass{article}

\usepackage[
  left=1cm,
  right=1cm,
  top=0.5cm,
  bottom=1cm,
  paper=a4paper,
  includeheadfoot
]{geometry}
\usepackage{framed}
\usepackage{pgfornament}
\usepackage{fancyhdr}
\usepackage{lastpage}

\definecolor{headercolor}{HTML}{000000}
\definecolor{leftbarcolor}{HTML}{0d10aa}

\renewcommand{\familydefault}{\sfdefault}

\renewenvironment{leftbar}[1][\hsize]
{
    \def\FrameCommand
    {
        {\color{leftbarcolor}\vrule width 3pt}%
        \hspace{0pt}%must no space.
        \fboxsep=\FrameSep\colorbox{white}%
    }
    \MakeFramed{\hsize#1\advance\hsize-\width\FrameRestore}
}
{\endMakeFramed}

\renewcommand\labelitemi{$\oplus$}

\pagestyle{fancy}\fancyhf{}\fancyfoot[C]{Page \thepage \hspace{1pt} of \pageref{LastPage}}

\setlength{\headheight}{1cm}

\fancyhead[L]{\normalsize segevmalool@berkeley.edu}
\fancyhead[C]{\Huge Segev Malool}
\fancyhead[R]{(925) 255-3481}

\begin{document}

\pagenumbering{arabic}

\center\Large\textbf{Awards and Certifications}

\begin{minipage}{\textwidth}\center\normalsize
  \vspace{0.3cm}  
  Ping Identity Excellence Award $|$ Capital One TechX Finalist $|$ UC Berkeley Fung Alumni Award \\
  \vspace{0.2cm}
  Ping Identity Certified Professional -- Ping Federate $|$ AWS Certified Solutions Architect $|$ CompTIA Security+
  \vspace{0.2cm}
\end{minipage}

\vspace{0.3cm}\center\Large\textbf{Technical Skills}

\begin{minipage}{\textwidth}\center\normalsize
  \vspace{0.3cm}
  Java $|$
  JavaScript $|$
  Python $|$
  Reactive and Event-Driven Programming \\
  \vspace{0.3cm}
  Build Tooling $|$ 
  Automated Quality Assurance $|$
  Automated Deployments $|$
  Cloud $|$ 
  Software Architecture\\
  \vspace{0.3cm}
  TLS $|$
  HTTPS $|$
  SOAP $|$
  OAuth2 $|$ 
  OpenID Connect $|$ 
  SAML $|$
  FIDO2 $|$ 
  Access Control
\end{minipage}

\vspace{0.5cm}\center\Large\textbf{Experience}
\vspace{0.2cm}\color{headercolor}

\flushleft\noindent\large\textbf{Lively, Inc.}\hfill\small{
  May 2022 -- Present $|$ San Francisco $|$ Full Time
}\color{black}

\begin{leftbar}
  \normalsize\textbf{Software Engineer} \hfill Platform and Card Services
  \begin{itemize}
    {\normalsize\setlength\itemindent{0.3cm}
    \item Designed and implemented application security improvements (mTLS, SNI, Secrets Management, AWS IAM).
    \item Demonstrated versatility by delivering product features across the technical stack (Typescript, Postgres).
    \item Elevated security of debit card systems integrations (Visa DPS, Fiserv).
    \item Drove operational excellence by collaborating with devops, security, and business managers.
    \item Enhanced observability by leading a transition from Datadog to Splunk (SIEM).
    \item Acquired specialized knowledge of Splunk, Docker, and Card Security, acted as SME in these areas.
    }
  \end{itemize}
\end{leftbar}

\flushleft\noindent\large\textbf{Fannie Mae}\hfill\small{
  Jan 2022 -- May 2022 $|$ Reston, VA $|$ Full Time
}\color{black}

\begin{leftbar}
  \normalsize\textbf{Software Engineer} \hfill Mortgage Commitment and Delivery
  \begin{itemize}
    {\normalsize\setlength\itemindent{0.3cm}
    \item Fortified mortgage commitment and delivery by architecting secure features across multiple Java applications.
    \item Established reliable and secure enterprise messaging by leveraging JPA, JAX, and Tibco EMS.
    \item Elevated software delivery and fortified security posture by skillfully leveraging enterprise Gradle integrations.
    }
  \end{itemize}
\end{leftbar}

\flushleft\noindent\large\textbf{Capital One}\hfill\small{
  Feb 2019 -- Jan 2022 $|$ McLean, VA $|$ Full Time
}\color{black}

\begin{leftbar}
  \normalsize\textbf{Software Engineer $\rightarrow$ Senior Software Engineer} \hfill Workforce Authentication and Machine Learning as a Service
  \begin{itemize}
    {\normalsize\setlength\itemindent{0.3cm}
    \item Pioneered cutting-edge machine learning for Capital One's MLaaS, fortifying data confidentiality and integrity.
    \item Orchestrated an award-winning deployment of PingFederate with robust enterprise integrations.
    \item Spearheaded an exploratory StrongKey FIDO2 Server (SKFS) deployment for passwordless authentication.
    \item Dramatically reduced cost by over 90\%, maintaining stringent security standards and seamless user experiences.
    \item Provided expert integration support and on-call incident response.
    \item Drove the widespread adoption of authentication best practices across 1100+ business applications.
    \item Led the seamless implementation of devops, source control, and AWS
      well-architected framework.
    \item Fostered a collaborative environment to address key technical challenges effectively.
    }
  \end{itemize}
\end{leftbar}

\flushleft\noindent\large\textbf{Clover Health}\hfill\small{
  Aug 2018 -- Jan 2019 $|$ San Francisco, CA $|$ Full Time
}\color{black}

\begin{leftbar}
  \normalsize\textbf{Data Operations Coordinator} \hfill Provider Data
  \begin{itemize}
    {\normalsize\setlength\itemindent{0.3cm}
    \item Verified, investigated and resolved provider data
      quality issues.
    \item Exemplified operational excellence by actively participating
      in data model review sessions.
    \item Engaged technical team to promote collaboration and
      cross-functional communication.
    }
  \end{itemize}
\end{leftbar}

\center\Large\textbf{Education}

\flushleft\noindent\large\textbf{UC Berkeley}\hfill\small{
  Jun 2017 -- Jun 2018 $|$ Berkeley, CA $|$ Full Time
}\color{black}

\begin{leftbar}
  \normalsize\textbf{Master of Engineering, Industrial Engineering and Operations Research}
  \begin{itemize}
    {\normalsize\setlength\itemindent{0.3cm}
    \item Completed interdisciplinary team projects in business and engineering.
    \item Completed coursework in data science, probability, and optimization analytics.
    \item Improved detection of arrhythmias in electrocardiogram data.
    }
  \end{itemize}
\end{leftbar}

\flushleft\noindent\large\textbf{UC Santa Barbara}\hfill\small{
  Jun 2014 -- Jun 2016 $|$ Santa Barbara, CA $|$ Full Time
}\color{black}

\begin{leftbar}
  \normalsize\textbf{Bachelor of Science, Statistical Science}
  \begin{itemize}
    {\normalsize\setlength\itemindent{0.3cm}
    \item Completed core coursework in probability modeling,
      statistical data analysis, and experiment design.
    \item Completed elective coursework in data mining, time series,
      formal languages, and graph/network theory.
    }
  \end{itemize}
\end{leftbar}

\flushleft\noindent\large\textbf{City College of San Francisco}\hfill\small{
  Jun 2012 -- Jun 2014 $|$ San Francisco, CA $|$ Full Time
}\color{black}

\begin{leftbar}
  \normalsize\textbf{Associate, Mathematics}
  \begin{itemize}
    {\normalsize\setlength\itemindent{0.3cm}
    \item Completed general education in science, language, and arts.
    \item Tutored mathematics from arithmetic through multivariable
      calculus for the CCSF Learning Assistance Center.
    \item Planned and executed lecture events on behalf of the CCSF
      Math Club.
    }
  \end{itemize}
\end{leftbar}

\end{document}
