\documentclass{article}

\usepackage[
  left=1cm,
  right=1cm,
  top=0.5cm,
  bottom=1cm,
  paper=a4paper,
  includeheadfoot
]{geometry}
\usepackage{framed}
\usepackage{pgfornament}
\usepackage{fancyhdr}
\usepackage{lastpage}

\definecolor{headercolor}{HTML}{000000}
\definecolor{leftbarcolor}{HTML}{0d10aa}

\renewcommand{\familydefault}{\sfdefault}

\renewenvironment{leftbar}[1][\hsize]
{
    \def\FrameCommand
    {
        {\color{leftbarcolor}\vrule width 3pt}%
        \hspace{0pt}%must no space.
        \fboxsep=\FrameSep\colorbox{white}%
    }
    \MakeFramed{\hsize#1\advance\hsize-\width\FrameRestore}
}
{\endMakeFramed}

\renewcommand\labelitemi{$\oplus$}

\pagestyle{fancy}\fancyhf{}\fancyfoot[C]{Page \thepage \hspace{1pt} of \pageref{LastPage} (please ask for full CV)}

\setlength{\headheight}{1cm}

\fancyhead[L]{\normalsize segbaus@gmail.com}
\fancyhead[C]{\Huge Segev Malool}
\fancyhead[R]{(925) 255-3481}

\begin{document}

\pagenumbering{arabic}

\center\Large\textbf{Awards and Certifications}
\begin{minipage}{\textwidth}\center\normalsize
  \vspace{0.3cm}
  Ping Identity Excellence Award $|$ Capital One TechX Finalist $|$ UC Berkeley Fung Alumni Award \\
  \vspace{0.2cm}
  Master of Engineering $|$ Ping Identity Certified Professional -- Ping Federate $|$ CompTIA Security+
  \vspace{0.2cm}
\end{minipage}

\vspace{0.3cm}\center\Large\textbf{Technical Skills}

\begin{minipage}{\textwidth}\center\normalsize
  \vspace{0.3cm}
  API Design $|$ 
  Cost Analysis $|$
  Relational Data Modeling $|$
  Statistical Data Modeling $|$
  Optimization Analytics $|$
  Enterprise Identity \\
  \vspace{0.3cm}
  Enterprise Platforms $|$
  Automated Quality Assurance $|$
  Automated Deployments $|$
  Cloud $|$
  Data Engineering $|$
  Access Control\\
  \vspace{0.3cm}
  Airflow $|$
  BigQuery $|$
  Splunk $|$
  Docker $|$
  Looker $|$
  Grafana $|$
  PingFederate $|$
  Okta $|$
  Intellij $|$
  Github\\
  \vspace{0.3cm}
  TLS (+ extensions) $|$
  HTTP/S $|$
  Tunneling/Proxy $|$
  SOAP $|$
  OAuth2 $|$ 
  OpenID Connect $|$ 
  SAML $|$
  SCIM $|$
  SCEP $|$
  FIDO2\\
  \vspace{0.3cm}
  Java $|$
  JavaScript/TypeScript $|$
  Python $|$
  Golang $|$
  LookML\\
\end{minipage}

\vspace{0.5cm}\center\Large\textbf{Experience}
\vspace{0.2cm}\color{headercolor}

\flushleft\noindent\large\textbf{Etsy}\hfill\small{
  Sept 2024 -- Present $|$ San Francisco $|$ Full Time
}\color{black}

\begin{leftbar}
  \normalsize\textbf{Senior Security and Software Engineer} \hfill Enterprise Security and Access Management
  \begin{itemize}
    {\normalsize\setlength\itemindent{0.3cm} 
        \item Implemented and integrated device trust program for over 2000 Mac OS and Windows devices.
        \item Designed and implemented a data pipeline for admin access usage, resulting in massive 50\% revocation rate.
        \item Designed and implemented a data pipeline for Okta System Logs, resulting in data-driven insights for 5 projects.
        \item Developed automated process for compliance tooling, saving hundreds of thousands of dollars in labor costs.
        \item Expertly supported app integrations based on identity standards, such as SAML and Okta provisioning/SCIM.
    }
  \end{itemize}
\end{leftbar}

\flushleft\noindent\large\textbf{Lively, Inc.}\hfill\small{
  May 2022 -- Sept 2024 $|$ San Francisco $|$ Full Time
}\color{black}

\begin{leftbar}
  \normalsize\textbf{Software Engineer} \hfill Backend, Platform, and Integrations
  \begin{itemize}
    {\normalsize\setlength\itemindent{0.3cm} 
        \item Implemented backend APIs for mobile, resulting in 4.9 stars at over 4500 ratings, an industry leading achievement.
        \item Collaborated with product marketing team to deliver affiliate partnerships for B2B referrals using Impact Radius.
        \item Urgently implemented a card usage detection algorithm which protected hundreds of thousands of dollars annually.
        \item Enhanced confidentiality and integrity of third party integrations using SAML, SFTP, and tunneling HTTPS/mTLS.
        \item Drove foundational software engineering advancements, elevating culture, cohesion and operational excellence.
    }
  \end{itemize}
\end{leftbar}

\flushleft\noindent\large\textbf{Fannie Mae}\hfill\small{
  Jan 2022 -- May 2022 $|$ Reston, VA $|$ Full Time
}\color{black}

\begin{leftbar}
  \normalsize\textbf{Software Engineer} \hfill Mortgage Commitment and Delivery
\end{leftbar}

\flushleft\noindent\large\textbf{Capital One}\hfill\small{
  Feb 2019 -- Jan 2022 $|$ McLean, VA $|$ Full Time
}\color{black}

\begin{leftbar}
  \normalsize\textbf{Software Engineer $\rightarrow$ Senior Software Engineer} \hfill Workforce Authentication (SSO) and Machine Learning as a Service
\end{leftbar}

\center\Large\textbf{Education}

\flushleft\noindent\large\textbf{UC Berkeley}\hfill\small{
  Jun 2017 -- Jun 2018 $|$ Berkeley, CA $|$ Full Time
}\color{black}

\normalsize{Master of Engineering, Industrial Engineering and Operations Research}

\flushleft\noindent\large\textbf{UC Santa Barbara}\hfill\small{
  Jun 2014 -- Jun 2016 $|$ Santa Barbara, CA $|$ Full Time
}\color{black}

\normalsize{Bachelor of Science, Statistical Science}

\end{document}
